---
title: "PROB_Goodness_of_Fit"
output:
  html_document: 
    toc: yes
    code_folding: hide
    df_print: paged
    highlight: espresso
    self_contained: yes
    theme: cosmo
    toc_float: yes
  pdf_document:
    keep_tex: true
date: "2025-10-19"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

maketitle <- function(name, L = 2)
{
  pander::pandoc.p('')
  pander::pandoc.header(name, level = L)
  pander::pandoc.p('')
  
}


library(tidyverse)
library (fixest)
library(kableExtra)
library(viridis)
library(stringi)
library(psych)
library(ggforce) # for 'geom_arc_bar'
library(ggrepel)
library(ggplot2)
library(cowplot)
library(knitr)
library(pander)
library(broom)
library(purrr)
panderOptions('digits', 3)
library(gt)
library(modelsummary)
library(rhdf5)
library(parallel)
library(patchwork)
library(readxl)
library(zoo)
#define not in operator
"%ni%"<-Negate("%in%")
## --- Paths (MNSC item 13: relative; run from the package root) ---------------
## Resolve the package root whether knit from the root or interactively from code/r,
## then load the central relative paths from config.R.
if (!file.exists("config.R") && file.exists("../../config.R")) {
  knitr::opts_knit$set(root.dir = normalizePath("../.."))
  setwd("../..")
}
source("config.R")              # path, data_dir, est_dir, table_dir, fig_dir
source("code/r/functions_V4.1.R")

# helper to standardize using stored mu/sdev
z <- function(x, nm) (x - mu[[nm]]) / sdev[[nm]]

start_date<-as.Date("1987-06-30") # sample start date

end_date=as.Date("2023-12-31") # sample end date


```

```{r import_data, echo=FALSE, message=FALSE, fig.width=24,fig.height=11,warning = FALSE, results='asis'}

PROB_Agg<-read_csv(paste0(data_dir, 'PROB_agg.csv'))

p<-PROB_Agg%>%select(-n_firms)%>%pivot_longer(cols=-date, names_to='var', values_to='value')%>%
  mutate(var=case_when(var=='PROB_ew'~'Equal Weighted',
                       var=='PROB_vw'~'Value Weighted'))%>%
  filter(var!='Equal Weighted')%>%
  ggplot(aes(x=date, y=value, color=var))+
  geom_line()+
  theme_minimal()+
  labs(title='Aggregate PROB variables', y='Value', x='Date')+
  mytheme_white

print(p)


```

```{r import aggregate default measure, echo=FALSE, message=FALSE, fig.width=24,fig.height=11,warning = FALSE, results='asis'}

CMDI<-read_xlsx(paste0(data_dir, 'Market_CMDI.xlsx'))

#Monthly
CMDI_monthly <- CMDI %>%
  mutate(month = floor_date(eow_friday, "month")) %>%      # group key
  group_by(month) %>%
  slice_max(eow_friday, n = 1, with_ties = FALSE) %>%      # last obs in that month
  ungroup() %>%
  mutate(date = ceiling_date(month, "month") - days(1)) %>%  # last calendar day
  select(date, everything(), -month)%>%
  rename(CMDI=Market,
         CMDIIG=IG,
         CMDIHY=HY)


Moodys<-read_xlsx(paste0(data_dir, 'Moodys_NB_QTRLy_US_Defaults_US_21072020.xlsx'))

Moodys<-Moodys <- Moodys %>%
  select("Étiquettes de lignes", "ALL")%>%
  mutate(
    qtr_std = str_replace(`Étiquettes de lignes`, "^\\s*(\\d{4})/QTR-(\\d)\\s*$", "\\1 Q\\2"),
    qtr_end = as.Date(as.yearqtr(qtr_std, format = "%Y Q%q"), frac = 1)
  ) %>%
  filter(!is.na(qtr_end)) %>%                # drop rows like the all-NA example
  select(date = qtr_end, everything(), -qtr_std, -`Étiquettes de lignes`)

BAML<-read_csv(paste0(data_dir,'BAMLC0A0CM.csv'))

colnames(BAML)<-c('date', 'OAS')

BAA<-read_csv(paste0(data_dir,'BAA10Y.csv'))

colnames(BAA)<-c('date', 'BAA')

BAA<-BAA %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(month) %>%
  slice_max(date, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(-month)%>%mutate(BAA=BAA/100, date=ceiling_date(date, "month") - days(1))


```

```{r merge correlations, echo=FALSE, message=FALSE, fig.width=24,fig.height=11,warning = FALSE, results='asis'}

prob_merged <- PROB_Agg %>%
  mutate(
    date        = as.Date(date)  ) %>%
  left_join(CMDI_monthly %>% mutate(date = as.Date(date)),
            by = 'date') %>%
  left_join(Moodys %>% mutate(date = as.Date(date)),
            by = 'date') %>%
  left_join(BAML %>% mutate(date = as.Date(date)),
            by = 'date') %>%
  left_join(BAA %>% mutate(date = as.Date(date)),
            by = 'date') %>%
  arrange(date)

prob_merged<-prob_merged%>%mutate(Moodys=ALL/n_firms)

prob_merged<-prob_merged%>%mutate(quarter=year(date)*100+quarter(date))

prob_merged<-prob_merged%>%arrange(quarter, date) %>% # or ticker, etc.
  group_by(quarter) %>%                               # group within quarter
  fill(Moodys, .direction = "up") %>%                 # backfill (next obs → current)
  ungroup() %>%
  select(-quarter)                                     

# Plot
p1<-prob_merged%>%ggplot(aes(x=date, y=CMDI))+
  geom_line()+
  theme_minimal()+
  labs(title='CMDI', y='value', x='Date')+
  scale_color_viridis(discrete=TRUE)+
  mytheme_white

p2<-prob_merged%>%ggplot(aes(x=date, y=OAS))+
  geom_line()+
  theme_minimal()+
  labs(title='OAS',y='value', x='Date')+
  scale_color_viridis(discrete=TRUE)+
  mytheme_white

p3<-prob_merged%>%
  filter(month(date)%in%c(3, 6, 9, 12))%>%
  ggplot(aes(x=date, y=Moodys))+
  geom_line()+
  theme_minimal()+
  labs(title='Moodys Default Rate',y='value', x='Date')+
  scale_color_viridis(discrete=TRUE)+
  mytheme_white

p4<-prob_merged%>%
  ggplot(aes(x=date, y=BAA))+
  geom_line()+
  theme_minimal()+
  labs(title='BAA Yield',y='value', x='Date')+
  scale_color_viridis(discrete=TRUE)+
  mytheme_white

print(p1|p2|p3|p4)

```

# Concurrent regressions

Aggregate distress measures to predict expected default in 12 months.

$PROB_{t}=\alpha+\beta_1 BAA_t+\beta_2Moodys + \beta_3 CMDI$

CMDI is only available starting from 2005. We perform full sample regression and split sample (Before vs after  2008-12-31) estimation. For each method, we standardize all predictors to zero mean and unit standard deviation, and calculate the fitted values using available predictors at each time. We consider two frequencies: for monthly fequency, we interpolate moody's default frequency in a given quarter to months in the quarter, or quarterly frequency in which no interpolation is needed.

```{r predictive regressions, echo=FALSE, message=FALSE, fig.width=24,fig.height=11,warning = FALSE, results='asis'}

# Full sample

maketitle('Full sample estimation', 2)

#Monthly

predictor_vars <- c("BAA","Moodys","CMDI")  # All predictors

# Standardize all predictors.
est_df <- prob_merged %>% select(PROB_vw, all_of(predictor_vars)) %>% drop_na()
mu <- sapply(est_df[predictor_vars], mean, na.rm = TRUE)
sdev <- sapply(est_df[predictor_vars], sd,   na.rm = TRUE)



# 2) Standardize entire dataset using those mu/sd
prob_z <- prob_merged %>%
  mutate(across(all_of(predictor_vars), ~ z(., cur_column())))

fml <- as.formula(paste("PROB_vw ~", paste(predictor_vars, collapse = " + ")))

mdl <- feols(fml, data =prob_z)

prob_z_pred <- prob_z %>%
  mutate(across(all_of(predictor_vars), ~ replace_na(., 0)))

plot_df <- prob_z_pred %>%
  mutate(Fitted = predict(mdl, newdata = .)) %>%
  rename(Logit=PROB_vw)%>%
  select(date, Logit, Fitted) %>%
  pivot_longer(c(Logit, Fitted), names_to = "series", values_to = "value")%>%
  filter(date<=end_date)

gfc_start <- as.Date("2007-09-30")
gfc_end   <- as.Date("2008-12-31")

p <- ggplot(plot_df, aes(x = date, y = value, color = series, linetype = series)) +
  # shaded GFC window (drawn first = underneath)
  annotate("rect",
           xmin = gfc_start, xmax = gfc_end,
           ymin = -Inf, ymax = Inf,
           fill = "grey50", alpha = 0.12) +
  geom_line() +
  geom_vline(xintercept = gfc_start, linetype = "dashed") +
  geom_vline(xintercept = gfc_end,   linetype = "dashed") +
  labs(x = "Date", y = "Value", title = "Monthly") +
    scale_color_manual(
    values = c(red, blue),
    name   = "Series",
    labels = c("Campbell et al. (2008)", "Fitted")
  ) +
   scale_linetype_manual(
    values = c("solid", "dashed"),
    name   = "Series",
    labels = c("Campbell et al. (2008)", "Fitted")
  ) +
  mytheme_white+
  ylim(0,0.002)

print(p)


ggsave(paste0(fig_dir, "fig_PROB_fit_All_2023.png"), p, width = 8, height = 6, dpi = 300)

#Quarterly Average of monthly values
p1 <- plot_df%>%mutate(quarter=year(date)*100+quarter(date))%>%
  group_by(quarter, series)%>%
  mutate(value=mean(value))%>%
  filter(month(date)%in%c(3, 6, 9, 12))%>%
  ggplot(aes(x = date, y = value, color = series, linetype = series)) +
  # shaded GFC window (drawn first = underneath)
  annotate("rect",
           xmin = gfc_start, xmax = gfc_end,
           ymin = -Inf, ymax = Inf,
           fill = "grey50", alpha = 0.12) +
  geom_line() +
  geom_vline(xintercept = gfc_start, linetype = "dashed") +
  geom_vline(xintercept = gfc_end,   linetype = "dashed") +
  labs(x = "Date", y = "Value", title = "Quarterly Average") +
    scale_color_manual(
    values = c(red, blue),
    name   = "Series",
    labels = c("Campbell et al. (2008)", "Fitted")
  ) +
   scale_linetype_manual(
    values = c("solid", "dashed"),
    name   = "Series",
    labels = c("Campbell et al. (2008)", "Fitted")
  ) +
  mytheme_white+
  ylim(0,0.002)

print(p1)

ggsave(paste0(fig_dir, "fig_PROB_fit_All_2023_qtr_avg.png"), p1, width = 8, height = 6, dpi = 300)


# Quarterly

predictor_vars <- c("BAA","Moodys","CMDI")  # All predictors

# Standardize all predictors.
est_df <- prob_merged%>%filter(month(date)%in%c(3, 6, 9, 12)) %>% select(PROB_vw, all_of(predictor_vars)) %>% drop_na()
mu <- sapply(est_df[predictor_vars], mean, na.rm = TRUE)
sdev <- sapply(est_df[predictor_vars], sd,   na.rm = TRUE)


# 2) Standardize entire dataset using those mu/sd
prob_z <- prob_merged %>%filter (month(date)%in%c(3, 6, 9, 12)) %>%
  mutate(across(all_of(predictor_vars), ~ z(., cur_column())))

fml <- as.formula(paste("PROB_vw ~", paste(predictor_vars, collapse = " + ")))

mdl <- feols(fml, data =prob_z)

prob_z_pred <- prob_z %>%
  mutate(across(all_of(predictor_vars), ~ replace_na(., 0)))

plot_df <- prob_z_pred %>%
  mutate(Fitted = predict(mdl, newdata = .)) %>%
  rename(Logit=PROB_vw)%>%
  select(date, Logit, Fitted) %>%
  pivot_longer(c(Logit, Fitted), names_to = "series", values_to = "value")%>%
  filter(date<=end_date)

gfc_start <- as.Date("2007-09-30")
gfc_end   <- as.Date("2008-12-31")

p2 <- ggplot(plot_df, aes(x = date, y = value, color = series, linetype = series)) +
  # shaded GFC window (drawn first = underneath)
  annotate("rect",
           xmin = gfc_start, xmax = gfc_end,
           ymin = -Inf, ymax = Inf,
           fill = "grey50", alpha = 0.12) +
  geom_line() +
  geom_vline(xintercept = gfc_start, linetype = "dashed") +
  geom_vline(xintercept = gfc_end,   linetype = "dashed") +
  labs(x = "Date", y = "Value", title = "Quarterly") +
    scale_color_manual(
    values = c(red, blue),
    name   = "Series",
    labels = c("Campbell et al. (2008)", "Fitted")
  ) +
   scale_linetype_manual(
    values = c("solid", "dashed"),
    name   = "Series",
    labels = c("Campbell et al. (2008)", "Fitted")
  ) +
  mytheme_white+
  ylim(0,0.002)

print(p2)

ggsave(paste0(fig_dir, "fig_PROB_fit_All_2023_qtr.png"), p2, width = 8, height = 6, dpi = 300)

#Correlation
df<-plot_df%>%pivot_wider(names_from=series, values_from=value)%>%mutate(subsample=ifelse(date<=as.Date("2008-12-31"), 'Pre-2009', 'Post-2008'))

fit_corr<-df%>%
  group_by(subsample)%>%
  summarize(
  corr=cor(Logit, Fitted, use='complete.obs')
)



combined<-p|p1|p2

print(combined)

ggsave(paste0(fig_dir, "fig_PROB_fit_Qtr_compare.png"), combined, width = 18, height = 6, dpi = 300)


maketitle('Split sample estimation', 2)


# Separate regressions for pre and post 2008

# Monthly-------

# Pre-2008

predictor_vars <- c("BAA","Moodys","CMDI")  # All predictors

# Standardize all predictors.
est_df <- prob_merged %>%filter(date<=as.Date("2008-12-31"))%>%select(PROB_vw, all_of(predictor_vars)) %>% drop_na()

mu <- sapply(est_df[predictor_vars], mean, na.rm = TRUE)
sdev <- sapply(est_df[predictor_vars], sd,   na.rm = TRUE)

# 2) Standardize entire dataset using those mu/sd
prob_z <- prob_merged %>% 
  filter(date<=as.Date("2008-12-31")) %>%
  mutate(across(all_of(predictor_vars), ~ z(., cur_column())))

fml <- as.formula(paste("PROB_vw ~", paste(predictor_vars, collapse = " + ")))

mdl <- feols(fml, data =prob_z)

prob_z_pred <- prob_z %>%
  mutate(across(all_of(predictor_vars), ~ replace_na(., 0)))

plot_df_pre2008 <- prob_z_pred %>%
  mutate(Fitted = predict(mdl, newdata = .)) %>%
  rename(Logit=PROB_vw)%>%
  select(date, Logit, Fitted) %>%
  pivot_longer(c(Logit, Fitted), names_to = "series", values_to = "value")%>%
  filter(date<=end_date)

# Post-2008
est_df <- prob_merged %>% filter(date > as.Date("2008-12-31"))%>% select(PROB_vw, all_of(predictor_vars)) %>% drop_na()

mu <- sapply(est_df[predictor_vars], mean, na.rm = TRUE)
sdev <- sapply(est_df[predictor_vars], sd,   na.rm = TRUE)


# 2) Standardize entire dataset using those mu/sd
prob_z <- prob_merged %>%filter(date > as.Date("2008-12-31"))%>%
  mutate(across(all_of(predictor_vars), ~ z(., cur_column())))

fml <- as.formula(paste("PROB_vw ~", paste(predictor_vars, collapse = " + ")))

mdl <- feols(fml, data =prob_z)

prob_z_pred <- prob_z %>%
  mutate(across(all_of(predictor_vars), ~ replace_na(., 0)))

plot_df_post2008 <- prob_z_pred %>%
  mutate(Fitted = predict(mdl, newdata = .)) %>%
  rename(Logit=PROB_vw)%>%
  select(date, Logit, Fitted) %>%
  pivot_longer(c(Logit, Fitted), names_to = "series", values_to = "value")%>%
  filter(date<=end_date)

plot_df<-bind_rows(plot_df_pre2008, plot_df_post2008)

p <- ggplot(plot_df, aes(x = date, y = value, color = series, linetype = series)) +
  # shaded GFC window (drawn first = underneath)
  annotate("rect",
           xmin = gfc_start, xmax = gfc_end,
           ymin = -Inf, ymax = Inf,
           fill = "grey50", alpha = 0.12) +
  geom_line() +
  geom_vline(xintercept = gfc_start, linetype = "dashed") +
  geom_vline(xintercept = gfc_end,   linetype = "dashed") +
  labs(x = "Date", y = "Value", title = "Monthly") +
    scale_color_manual(
    values = c(red, blue),
    name   = "Series",
    labels = c("Campbell et al. (2008)", "Fitted")
  ) +
   scale_linetype_manual(
    values = c("solid", "dashed"),
    name   = "Series",
    labels = c("Campbell et al. (2008)", "Fitted")
  ) +
  mytheme_white+
  ylim(0,0.002)

print(p)

ggsave(paste0(fig_dir, "fig_PROB_fit_All_split.png"), p, width = 8, height = 6, dpi = 300)

# Quarterly average of the same thing--------

p1 <- plot_df%>%mutate(quarter=year(date)*100+quarter(date))%>%
  group_by(quarter, series)%>%
  mutate(value=mean(value))%>%
  filter(month(date)%in%c(3, 6, 9, 12))%>%
  ggplot(aes(x = date, y = value, color = series, linetype = series)) +
  # shaded GFC window (drawn first = underneath)
  annotate("rect",
           xmin = gfc_start, xmax = gfc_end,
           ymin = -Inf, ymax = Inf,
           fill = "grey50", alpha = 0.12) +
  geom_line() +
  geom_vline(xintercept = gfc_start, linetype = "dashed") +
  geom_vline(xintercept = gfc_end,   linetype = "dashed") +
  labs(x = "Date", y = "Value", title = "Quarterly Average") +
    scale_color_manual(
    values = c(red, blue),
    name   = "Series",
    labels = c("Campbell et al. (2008)", "Fitted")
  ) +
   scale_linetype_manual(
    values = c("solid", "dashed"),
    name   = "Series",
    labels = c("Campbell et al. (2008)", "Fitted")
  ) +
  mytheme_white+
  ylim(0,0.002)

print(p1)

ggsave(paste0(fig_dir, "fig_PROB_fit_All_split_qtr_avg.png"), p1, width = 8, height = 6, dpi = 300)


#---------

# Quarterly-------

# Pre-2008

predictor_vars <- c("BAA","Moodys","CMDI")  # All predictors

# Standardize all predictors.
est_df <- prob_merged %>%filter(date<=as.Date("2008-12-31")&month(date)%in%c(3, 6, 9, 12))%>%select(PROB_vw, all_of(predictor_vars)) %>% drop_na()

mu <- sapply(est_df[predictor_vars], mean, na.rm = TRUE)
sdev <- sapply(est_df[predictor_vars], sd,   na.rm = TRUE)

# 2) Standardize entire dataset using those mu/sd
prob_z <- prob_merged %>% 
  filter(date<=as.Date("2008-12-31")&month(date)%in%c(3, 6, 9, 12)) %>%
  mutate(across(all_of(predictor_vars), ~ z(., cur_column())))

fml <- as.formula(paste("PROB_vw ~", paste(predictor_vars, collapse = " + ")))

mdl <- feols(fml, data =prob_z)

prob_z_pred <- prob_z %>%
  mutate(across(all_of(predictor_vars), ~ replace_na(., 0)))

plot_df_pre2008 <- prob_z_pred %>%
  mutate(Fitted = predict(mdl, newdata = .)) %>%
  rename(Logit=PROB_vw)%>%
  select(date, Logit, Fitted) %>%
  pivot_longer(c(Logit, Fitted), names_to = "series", values_to = "value")%>%
  filter(date<=end_date)

# Post-2008
est_df <- prob_merged %>% filter(date > as.Date("2008-12-31")&month(date)%in%c(3, 6, 9, 12))%>% select(PROB_vw, all_of(predictor_vars)) %>% drop_na()

mu <- sapply(est_df[predictor_vars], mean, na.rm = TRUE)
sdev <- sapply(est_df[predictor_vars], sd,   na.rm = TRUE)


# 2) Standardize entire dataset using those mu/sd
prob_z <- prob_merged %>%filter(date > as.Date("2008-12-31")&month(date)%in%c(3, 6, 9, 12))%>%
  mutate(across(all_of(predictor_vars), ~ z(., cur_column())))

fml <- as.formula(paste("PROB_vw ~", paste(predictor_vars, collapse = " + ")))

mdl <- feols(fml, data =prob_z)

prob_z_pred <- prob_z %>%
  mutate(across(all_of(predictor_vars), ~ replace_na(., 0)))

plot_df_post2008 <- prob_z_pred %>%
  mutate(Fitted = predict(mdl, newdata = .)) %>%
  rename(Logit=PROB_vw)%>%
  select(date, Logit, Fitted) %>%
  pivot_longer(c(Logit, Fitted), names_to = "series", values_to = "value")%>%
  filter(date<=end_date)

plot_df<-bind_rows(plot_df_pre2008, plot_df_post2008)

p2 <- ggplot(plot_df, aes(x = date, y = value, color = series, linetype = series)) +
  # shaded GFC window (drawn first = underneath)
  annotate("rect",
           xmin = gfc_start, xmax = gfc_end,
           ymin = -Inf, ymax = Inf,
           fill = "grey50", alpha = 0.12) +
  geom_line() +
  geom_vline(xintercept = gfc_start, linetype = "dashed") +
  geom_vline(xintercept = gfc_end,   linetype = "dashed") +
  labs(x = "Date", y = "Default Probability", title = "") +
    scale_color_manual(
    values = c(red, blue),
    name   = "Series",
    labels = c("Campbell et al. (2008)", "Fitted")
  ) +
   scale_linetype_manual(
    values = c("solid", "dashed"),
    name   = "Series",
    labels = c("Campbell et al. (2008)", "Fitted")
  ) +
  mytheme_white+
  theme(legend.position = "bottom")+
  ylim(0,0.002)

print(p2)

#Correlation
df<-plot_df%>%pivot_wider(names_from=series, values_from=value)%>%mutate(subsample=ifelse(date<=as.Date("2008-12-31"), 'Pre-2009', 'Post-2008'))

fit_corr_split<-df%>%
  group_by(subsample)%>%
  summarize(
  corr=cor(Logit, Fitted, use='complete.obs')
)



ggsave(paste0(fig_dir, "fig_PROB_fit_All_split_qtr.png"), p2, width = 8, height = 6, dpi = 300)

combined<-p|p1|p2

print(combined)

ggsave(paste0(fig_dir, "fig_PROB_fit_split_Qtr_compare.png"), combined, width = 18, height = 6, dpi = 300)




```


